### 2017-08-19 paper/incomeShocks-jde-r1.tex
Add full OLS/community fixed effects tables for Appendix

\caption{Full OLS and Community Fixed Effects Results for Fertility Outcomes}
\label{tab:ols_fertility}
\begin{tabular}{@{} l D{.}{.}{2.6} D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6} @{}}
                                                       &\multicolumn{2}{c}{Currently pregnant}&\multicolumn{2}{c}{Birth since last survey}\\ \cmidrule(lr){2-3} \cmidrule(lr){4-5}
                                                       &                     & \mco{Community}     &                     & \mco{Community}      \\ 
                                                       & \mco{OLS}           & \mco{Fixed Effects} & \mco{OLS}           & \mco{Fixed Effects}  \\ 
\midrule
Crop loss - 1-7 months (200 TZS or above)              &      -0.053         &      -0.074\sym{*}  &                     &                     \\
                                                       &     (0.038)         &     (0.039)         &                     &                     \\
Crop loss - 7-14 months (200 TZS or above)             &                     &                     &      -0.103\sym{***}&      -0.115\sym{***}\\
                                                       &                     &                     &     (0.040)         &     (0.042)         \\
Assets per capita in wave 1 (10,000 TZS)               &      -0.001         &      -0.002\sym{**} &       0.000         &       0.001         \\
                                                       &     (0.001)         &     (0.001)         &     (0.001)         &     (0.001)         \\
1 - 6 years of education                               &      -0.011         &      -0.005         &       0.006         &       0.006         \\
                                                       &     (0.027)         &     (0.027)         &     (0.029)         &     (0.032)         \\
7 plus years of education                              &      -0.016         &       0.002         &       0.026         &       0.042         \\
                                                       &     (0.028)         &     (0.029)         &     (0.029)         &     (0.029)         \\
Age 23-27                                              &       0.017         &       0.022         &      -0.036         &      -0.027         \\
                                                       &     (0.033)         &     (0.036)         &     (0.033)         &     (0.032)         \\
Age 28-32                                              &      -0.037         &      -0.033         &      -0.060\sym{*}  &      -0.059\sym{*}  \\
                                                       &     (0.031)         &     (0.034)         &     (0.034)         &     (0.034)         \\
Age 33-37                                              &      -0.079\sym{**} &      -0.068\sym{**} &      -0.055         &      -0.057         \\
                                                       &     (0.032)         &     (0.034)         &     (0.035)         &     (0.036)         \\
Age 38-45                                              &      -0.174\sym{***}&      -0.156\sym{***}&      -0.184\sym{***}&      -0.194\sym{***}\\
                                                       &     (0.034)         &     (0.036)         &     (0.032)         &     (0.035)         \\
Constant                                               &       0.270\sym{***}&       0.293\sym{***}&       0.278\sym{***}&       0.237\sym{**} \\
                                                       &     (0.048)         &     (0.091)         &     (0.048)         &     (0.103)         \\
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Community fixed effects                                &    \mco{No}         &    \mco{Yes}        &    \mco{No}         &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{No }        &    \mco{No }        &    \mco{No }        &    \mco{No }        \\
Observations                                           &    \mco{988}        &    \mco{741}        &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\

\begin{table}[htbp]
\begin{center}
\begin{footnotesize}
\begin{threeparttable}
\caption{Full OLS and Community Fixed Effects Results for Contraceptive Use}
\label{tab:ols_contraceptive}
\begin{tabular}{@{} l D{.}{.}{2.6} D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6}  @{}}
\toprule
                                                       &                    \mct{Any}              &  \mct{Traditional}                        & \mct{Modern}        \\  \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
                                                       &                     & \mco{Community}     &                     & \mco{Community}     &                     & \mco{Community}      \\ 
                                                       & \mco{OLS}           & \mco{Fixed Effects} & \mco{OLS}           & \mco{Fixed Effects} & \mco{OLS}           & \mco{Fixed Effects}  \\

\midrule
Crop loss - 1-7 months                                 &       0.061\sym{**} &       0.059\sym{**} &       0.052\sym{**} &       0.048\sym{**} &      -0.001         &       0.004         \\
\hs (200 TZS or above)                                 &     (0.027)         &     (0.027)         &     (0.023)         &     (0.022)         &     (0.014)         &     (0.013)         \\
Assets per capita in wave 1                            &       0.001         &       0.001         &       0.001         &       0.001         &       0.001         &       0.000         \\
\hs (10,000 TZS)                                       &     (0.001)         &     (0.001)         &     (0.001)         &     (0.001)         &     (0.001)         &     (0.001)         \\
1 - 6 years of education                               &       0.025         &      -0.015         &       0.012         &      -0.020         &       0.020         &       0.003         \\
                                                       &     (0.022)         &     (0.023)         &     (0.019)         &     (0.020)         &     (0.013)         &     (0.015)         \\
7 plus years of education                              &       0.123\sym{***}&       0.095\sym{***}&       0.076\sym{**} &       0.056\sym{*}  &       0.058\sym{***}&       0.035\sym{**} \\
                                                       &     (0.035)         &     (0.036)         &     (0.030)         &     (0.030)         &     (0.019)         &     (0.016)         \\
Age 23-27                                              &       0.013         &       0.016         &       0.005         &       0.024         &       0.021         &      -0.000         \\
                                                       &     (0.037)         &     (0.038)         &     (0.024)         &     (0.028)         &     (0.030)         &     (0.023)         \\
Age 28-32                                              &       0.074\sym{*}  &       0.060         &       0.059\sym{*}  &       0.066\sym{*}  &       0.032         &      -0.012         \\
                                                       &     (0.039)         &     (0.044)         &     (0.033)         &     (0.039)         &     (0.021)         &     (0.019)         \\
Age 33-37                                              &       0.072\sym{*}  &       0.075\sym{*}  &       0.061\sym{*}  &       0.084\sym{**} &       0.048\sym{*}  &       0.018         \\
                                                       &     (0.040)         &     (0.043)         &     (0.035)         &     (0.036)         &     (0.029)         &     (0.023)         \\
Age 38-45                                              &       0.045         &       0.044         &       0.033         &       0.028         &       0.024         &       0.010         \\
                                                       &     (0.047)         &     (0.061)         &     (0.038)         &     (0.047)         &     (0.021)         &     (0.022)         \\
Constant                                               &      -0.005         &      -0.014         &       0.007         &      -0.002         &      -0.021         &      -0.017         \\
                                                       &     (0.040)         &     (0.065)         &     (0.035)         &     (0.056)         &     (0.018)         &     (0.024)         \\
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Community dummies                                      &    \mco{No}         &    \mco{Yes}        &    \mco{No}         &    \mco{Yes}        &    \mco{No}         &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{No }        &    \mco{No }        &    \mco{No }        &    \mco{No }        &    \mco{No }        &    \mco{No }        \\
Observations                                           &    \mco{988}        &    \mco{988}        &    \mco{988}        &    \mco{988}        &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\begin{tablenotes} \tiny
\end{footnotesize}

>>>>

% Pregnancy and birth results
\input{../tables/appendix_pregnant_birth.tex}

% Contraceptives results
\input{../tables/appendix_contraceptives.tex}
